New and simplified manual controls for projection and slice tours, with application to exploring classification boundaries in high dimensions

### 2023-01-19 paper/paper.Rmd
fig 5 and 6 modified

We start by a comparison of the two models and the data distribution shifting to $\mathbf{c}^{+}$, thus the slice is localized towards high values of bill depth in Figure \ref{slice1p}. We can see that all three slices (the two models and the data) contain almost no points from the third class (Gentoo), and that the decision boundary between the two models is very similar.

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.95\textwidth]{figures/slice1_p.pdf}}
%\centerline{\includegraphics[width=0.32\textwidth]{figures/slice1_p_rf.png}
%\includegraphics[width=0.32\textwidth]{figures/slice1_p_lda.png}
%\includegraphics[width=0.32\textwidth]{figures/slice1_p_data.png}}
\caption{Shifting the slice center allows for exploring the boundary in different subspaces. Here the center has been shifted out along the axis of bill depth (icon display at right represents slice center position). This region has no Gentoo. The two models have similar boundaries except that the RF is has a step shift in the middle.}
\label{slice1p}
\end{figure*}

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.32\textwidth]{figures/slice1_m_rf.png}
\includegraphics[width=0.32\textwidth]{figures/slice1_m_lda.png}
\includegraphics[width=0.32\textwidth]{figures/slice1_m_data.png}}
\caption{Shifting the slice center in the negative direction of bill depth produces regions that are mostly Gentoo. The two models have very different boundaries: the nonlinear potential of RF can be seen here where still some subspaces would predict to be Adelie and Chinstrap.}
\label{slice1m}
\end{figure*}

A more interesting comparison is found for $\mathbf{c}^{-}$, thus the slice localized towards low values of bill depth, shown in Figure \ref{slice1m}. The RF model (left) predicts all three species within this slice, with an interesting boundary for the third class (Gentoo). On the other hand the LDA model (middle) predominantly predicts the third class within the slice, this appears to be enforced through the linear structure of the model. Looking finally at the thick slice through the data we see that there are primarily observations from this class within the slice we can conclude that the two models have filled in the "empty" space (where we do not have any training observations) in very different ways and according to what we might expect given the model structure.

Finally it is interesting to compare the slice views to the projection of the models seen in Fig. \ref{proj1} to better understand how the boundaries change along the `bd` direction and where the differences in the projections come from.

>>>>

We start by a comparison of the two models and the data distribution shifting to $\mathbf{c}^{+}$, thus the slice is localized towards high values of bill depth in top row of Figure \ref{slice1p}. We can see that all three slices (the two models and the data) contain almost no points from the third class (Gentoo), and that the decision boundary between the two models is very similar.

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.95\textwidth]{figures/slice1_p.pdf}}
%\centerline{\includegraphics[width=0.32\textwidth]{figures/slice1_p_rf.png}
%\includegraphics[width=0.32\textwidth]{figures/slice1_p_lda.png}
%\includegraphics[width=0.32\textwidth]{figures/slice1_p_data.png}}
\caption{Shifting the slice center allows for exploring the boundary in different subspaces. Here the center has been shifted along the axis of `bd` (icon display at right represents slice center position). (Top row) Center is at large values of `bd`, showing a region with no Gentoo. The two models have similar boundaries except that the LDA is more linear. (Bottom row) Center is at small values of `bd`, reveals a region where the models differ substantially. The RF model carves some area for Adelie, but LDA would only predict to be Gentoo or Chinstrap here. LDA better matches the observed data in this region.}
\label{slice1p}
\end{figure*}

<!--
\begin{figure*}[ht]
\centerline{\includegraphics[width=0.32\textwidth]{figures/slice1_m_rf.png}
\includegraphics[width=0.32\textwidth]{figures/slice1_m_lda.png}
\includegraphics[width=0.32\textwidth]{figures/slice1_m_data.png}}
\caption{Shifting the slice center in the negative direction of bill depth produces regions that are mostly Gentoo. The two models have very different boundaries: the nonlinear potential of RF can be seen here where still some subspaces would predict to be Adelie and Chinstrap.}
\label{slice1m}
\end{figure*}
-->

A more interesting comparison is found for $\mathbf{c}^{-}$, thus the slice localized towards low values of bill depth, shown in the bottom row of Figure \ref{slice1p}. The RF model (left) predicts all three species within this slice, with an interesting boundary for the third class (Gentoo). On the other hand the LDA model (middle) predominantly predicts the third class within the slice, this appears to be enforced through the linear structure of the model. Looking finally at the thick slice through the data we see that there are primarily observations from this class within the slice we can conclude that the two models have filled in the "empty" space (where we do not have any training observations) in very different ways and according to what we might expect given the model structure.

Finally, it is interesting to compare the slice views to the projection of the models seen in Fig. \ref{proj1} to better understand how the boundaries change along the `bd` direction and where the differences in the projections come from.

### 2023-01-19 paper/paper.tex
fig 5 and 6 modified

We start by a comparison of the two models and the data distribution
shifting to \(\mathbf{c}^{+}\), thus the slice is localized towards high
values of bill depth in Figure \ref{slice1p}. We can see that all three
slices (the two models and the data) contain almost no points from the
third class (Gentoo), and that the decision boundary between the two
models is very similar.

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.95\textwidth]{figures/slice1_p.pdf}}
%\centerline{\includegraphics[width=0.32\textwidth]{figures/slice1_p_rf.png}
%\includegraphics[width=0.32\textwidth]{figures/slice1_p_lda.png}
%\includegraphics[width=0.32\textwidth]{figures/slice1_p_data.png}}
\caption{Shifting the slice center allows for exploring the boundary in different subspaces. Here the center has been shifted out along the axis of bill depth (icon display at right represents slice center position). This region has no Gentoo. The two models have similar boundaries except that the RF is has a step shift in the middle.}
\label{slice1p}
\end{figure*}

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.32\textwidth]{figures/slice1_m_rf.png}
\includegraphics[width=0.32\textwidth]{figures/slice1_m_lda.png}
\includegraphics[width=0.32\textwidth]{figures/slice1_m_data.png}}
\caption{Shifting the slice center in the negative direction of bill depth produces regions that are mostly Gentoo. The two models have very different boundaries: the nonlinear potential of RF can be seen here where still some subspaces would predict to be Adelie and Chinstrap.}
\label{slice1m}
\end{figure*}

A more interesting comparison is found for \(\mathbf{c}^{-}\), thus the
slice localized towards low values of bill depth, shown in Figure
\ref{slice1m}. The RF model (left) predicts all three species within
this slice, with an interesting boundary for the third class (Gentoo).
On the other hand the LDA model (middle) predominantly predicts the
third class within the slice, this appears to be enforced through the
linear structure of the model. Looking finally at the thick slice
through the data we see that there are primarily observations from this
class within the slice we can conclude that the two models have filled
in the ``empty'' space (where we do not have any training observations)
in very different ways and according to what we might expect given the
model structure.

Finally it is interesting to compare the slice views to the projection
of the models seen in Fig. \ref{proj1} to better understand how the
boundaries change along the \texttt{bd} direction and where the
differences in the projections come from.

>>>>

We start by a comparison of the two models and the data distribution
shifting to \(\mathbf{c}^{+}\), thus the slice is localized towards high
values of bill depth in top row of Figure \ref{slice1p}. We can see that
all three slices (the two models and the data) contain almost no points
from the third class (Gentoo), and that the decision boundary between
the two models is very similar.

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.95\textwidth]{figures/slice1_p.pdf}}
%\centerline{\includegraphics[width=0.32\textwidth]{figures/slice1_p_rf.png}
%\includegraphics[width=0.32\textwidth]{figures/slice1_p_lda.png}
%\includegraphics[width=0.32\textwidth]{figures/slice1_p_data.png}}
\caption{Shifting the slice center allows for exploring the boundary in different subspaces. Here the center has been shifted along the axis of `bd` (icon display at right represents slice center position). (Top row) Center is at large values of `bd`, showing a region with no Gentoo. The two models have similar boundaries except that the LDA is more linear. (Bottom row) Center is at small values of `bd`, reveals a region where the models differ substantially. The RF model carves some area for Adelie, but LDA would only predict to be Gentoo or Chinstrap here. LDA better matches the observed data in this region.}
\label{slice1p}
\end{figure*}

A more interesting comparison is found for \(\mathbf{c}^{-}\), thus the
slice localized towards low values of bill depth, shown in the bottom
row of Figure \ref{slice1p}. The RF model (left) predicts all three
species within this slice, with an interesting boundary for the third
class (Gentoo). On the other hand the LDA model (middle) predominantly
predicts the third class within the slice, this appears to be enforced
through the linear structure of the model. Looking finally at the thick
slice through the data we see that there are primarily observations from
this class within the slice we can conclude that the two models have
filled in the ``empty'' space (where we do not have any training
observations) in very different ways and according to what we might
expect given the model structure.

Finally, it is interesting to compare the slice views to the projection
of the models seen in Fig. \ref{proj1} to better understand how the
boundaries change along the \texttt{bd} direction and where the
differences in the projections come from.
